\thetitle

### 2021-05-04 paper/paper.tex
update

% \MS[t]{todo} We evaluate two different kinds of reward reporting as they have been proposed by
% \cite{Schneckenreither2019}. They find that it is beneficial to overcome the time offset imposed by
% the production system. That is, although orders are immediately released to the production system
% and thus generate a response in terms of a reward to the agent, the full impact of the chosen action
% takes several periods to materialise. For instance, by deciding not to release an order, which later
% becomes a backorder, it is beneficial to reward the actions actually responsible for the backorder
% instead of the last action (only). Thus they propose to keep track of the orders currently in the
% order pool until all fully traversed through the production system and reward the actions according
% to all orders in the order pool.

@@

      \ql{0.99}      & \cost{38563.000}  & \cost{134703.600} & \cost{81704.800}   & \fgiboc{134703.600}{81704.800}  & \cost{254971.400}  & \timem{1.335} & \fgit{1.335}{2.558} & \tard{0.094} & \costpp{254971.400}  &                    \\

@@

      \rl{1.00}      & \cost{38659.100}  & \cost{156659.200} & \cost{59743.200}   & \fgiboc{156659.200}{59743.200}  & \cost{255061.500}  & \timem{1.338} & \fgit{1.338}{2.678} & \tard{0.068} & \costpp{255061.500}  & \rnd{36.501}       \\

@@

      \rl{1.00}      & \cost{60778.500}  & \cost{234045.000} & \cost{76168.000}   & \fgiboc{234045.000}{76168.000}  & \cost{370991.500}  & \timem{1.637} & \fgit{1.637}{3.226} & \tard{0.066} & \costpp{370991.500}  & \rnd{52.291}       \\

@@

      \BILThree{}    & \cost{51976.550}  & \cost{240175.000} & \cost{77822.400}   & \fgiboc{240175.000}{77822.400}  & \cost{369973.950}  & \timem{1.475} & \fgit{1.475}{3.091} & \tard{0.060} & \costpp{369973.950}  &                    \\

@@

      \ql{0.99}      & \cost{98909.150}  & \cost{190681.000} & \cost{297333.600}  & \fgiboc{190681.000}{297333.600} & \cost{586923.750}  & \timem{2.133} & \fgit{2.133}{3.417} & \tard{0.173} & \costpp{586923.750}  &                    \\
      \rl{0.99}      & \cost{105348.200} & \cost{263950.600} & \cost{207183.200}  & \fgiboc{263950.600}{207183.200} & \textbf{\cost{576482.000}}  & \timem{2.238} & \fgit{2.238}{3.825} & \tard{0.121} & \textbf{\costpp{576482.000}}  & \rnd{79.826}       \\
      \rl{1.00}      & \cost{107873.800} & \cost{240798.800} & \cost{253865.600}  & \fgiboc{240798.800}{253865.600} & \cost{602538.200}  & \timem{2.280} & \fgit{2.280}{3.771} & \tard{0.153} & \costpp{602538.200}  & \rnd{80.425}       \\

@@

      \BILThree{}    & \cost{88252.450}  & \cost{207210.600} & \cost{299885.600}  & \fgiboc{207210.600}{299885.600} & \cost{595348.650}  & \timem{1.957} & \fgit{1.957}{3.309} & \tard{0.148} & \costpp{595348.650}  &                    \\

@@

    distributed demand interarrival times. }

@@

      \ql{0.99}   & \cost{53873.500} & \cost{142398.800} & \cost{164427.200} & \fgiboc{142398.800}{164427.200}  & \cost{360699.500} & \timem{1.585} & \fgit{1.585}{2.796}  & \tard{0.162} & \costpp{360699.500} & \\

@@

      \BILTwo{}   & \cost{48618.850} & \cost{ 66927.200} & \cost{248638.400} & \fgiboc{ 66927.200}{248638.400}  & \cost{364184.450} & \timem{1.480} & \fgit{1.480}{2.312}  & \tard{0.220} & \costpp{364184.450} & \\

@@

      \ql{0.99}   & \cost{87706.700} & \cost{227485.400} & \cost{225150.400} & \fgiboc{227485.400}{225150.400}  & \cost{540342.500} & \timem{2.043} & \fgit{2.043}{3.541}  & \tard{0.166} & \costpp{540342.500} & \\
      \rl{0.99}   & \cost{89838.950} & \cost{253476.000} & \cost{185687.200} & \fgiboc{253476.000}{185687.200}  & \cost{529002.150} & \timem{2.078} & \fgit{2.078}{3.689}  & \tard{0.124} & \costpp{529002.150} & \rnd{70.527} \\
      \rl{1.00}   & \cost{87171.500} & \cost{242915.600} & \cost{198456.000} & \fgiboc{242915.600}{198456.000}  & \cost{528543.100} & \timem{2.034} & \fgit{2.034}{3.599} & \tard{0.134} & \costpp{528543.100} & \rnd{72.944} \\

@@

      \BILThree{} & \cost{79029.850} & \cost{200273.200} & \cost{242100.800} & \fgiboc{200273.200}{242100.800}  & \textbf{\cost{521403.850}} & \timem{1.890} & \fgit{1.890}{3.265}  & \tard{0.142} & \textbf{\costpp{521403.850}} & \\

@@

      \ql{0.99}   & \cost{168655.950} & \cost{222145.800} & \cost{788662.400} & \fgiboc{222145.800}{788662.400}  & \cost{1179464.150} & \timem{3.134} & \fgit{3.134}{4.501}  & \tard{0.285} & \costpp{1179464.150} & \\
      \rl{0.99}   & \cost{158034.800} & \cost{212726.200} & \cost{701300.800} & \fgiboc{212726.200}{701300.800}  & \cost{1072061.800} & \timem{2.970} & \fgit{2.970}{4.300}  & \tard{0.281} & \costpp{1072061.800} & \rnd{115.801} \\

@@

      \BILThree{} & \cost{144278.250} & \cost{154146.800} & \cost{877450.400} & \fgiboc{154146.800}{877450.400}  & \cost{1175875.450} & \timem{2.756} & \fgit{2.756}{3.857}  & \tard{0.294} & \costpp{1175875.450} & \\
      \BILFour{}  & \cost{147077.800} & \cost{335070.400} & \cost{622141.600} & \fgiboc{335070.400}{622141.600}  & \cost{1104289.800} & \timem{2.800} & \fgit{2.800}{4.608}  & \tard{0.175} & \costpp{1104289.800} & \\

@@

    distributed interarrival times of the demand. }

@@

@@

\section{}

\begin{table}
  \begin{center}
    \begin{tabular}{lP{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}}
      \toprule
      70-\(\Unif\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 3.37e-04  &           &           &           &           &             \\
      \rl{1.0}     & 3.55e-01  & 1.04e-05  &           &           &           &             \\
      \BILOne{}    & 1.94e-45  & 2.48e-51  & 6.90e-44  &           &           &             \\
      \BILTwo{}    & 1.09e-24  & 3.35e-16  & 9.57e-27  & 3.66e-64  &           &             \\
      \BILThree{}  & 1.78e-20  & 9.27e-29  & 2.44e-18  & 1.35e-22  & 6.26e-47  &             \\
      \BILFour{}   & 6.30e-34  & 3.85e-41  & 4.83e-32  & 1.16e-08  & 3.00e-56  & 1.16e-08    \\
      \bottomrule
      \toprule
      80-\(\Unif\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 4.78e-16  &           &           &           &           &             \\
      \rl{1.00}    & 5.26e-04  & 3.96e-08  &           &           &           &             \\
      \BILOne{}    & 1.02e-40  & 1.98e-21  & 3.92e-34  &           &           &             \\
      \BILTwo{}    & 6.98e-10  & 7.12e-03  & 2.06e-03  & 1.31e-27  &           &             \\
      \BILThree{}  & 2.16e-02  & 8.93e-11  & 2.03e-01  & 1.57e-36  & 2.46e-05  &             \\
      \BILFour{}   & 6.16e-33  & 1.10e-11  & 2.74e-25  & 5.33e-05  & 5.38e-18  & 5.30e-28    \\
      \bottomrule
      \toprule
      90-\(\Unif\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 5.18e-01  &           &           &           &           &             \\
      \rl{1.00}    & 1.94e-04  & 1.56e-05  &           &           &           &             \\
      \BILOne{}    & 8.40e-42  & 9.61e-43  & 1.10e-34  &           &           &             \\
      \BILTwo{}    & 2.36e-33  & 1.10e-34  & 5.21e-25  & 1.56e-05  &           &             \\
      \BILThree{}  & 4.16e-04  & 3.64e-05  & 8.19e-01  & 6.27e-35  & 1.81e-25  &             \\
      \BILFour{}   & 2.33e-20  & 6.57e-22  & 1.79e-11  & 2.93e-18  & 4.39e-08  & 5.97e-12    \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:stats-unif}Results from the statistical analysis for the results of of
    moderate variability in the system. }
\end{table}

\begin{table}
  \begin{center}
    \begin{tabular}{lP{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}}
      \toprule
      70-\(\Exp\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}   & 1.75e-02  &           &           &           &           &             \\
      \rl{1.00}   & 6.15e-07  & 5.50e-12  &           &           &           &             \\
      \BILOne{}   & 7.62e-35  & 1.74e-39  & 1.32e-23  &           &           &             \\
      \BILTwo{}   & 3.33e-01  & 1.02e-03  & 3.17e-05  & 6.06e-33  &           &             \\
      \BILThree{} & 5.96e-17  & 1.79e-11  & 6.09e-29  & 7.00e-52  & 3.47e-19  &             \\
      \BILFour{}  & 1.16e-24  & 6.25e-30  & 1.68e-12  & 4.68e-06  & 1.56e-22  & 3.43e-44    \\
      \bottomrule
      \toprule
      80-\(\Exp\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \bottomrule
      \rl{0.99}   & 7.07e-02  &           &           &           &           &             \\
      \rl{1.00}   & 1.74e-03  & 1.72e-01  &           &           &           &             \\
      \BILOne{}   & 2.39e-35  & 6.77e-39  & 2.38e-41  &           &           &             \\
      \BILTwo{}   & 1.22e-25  & 1.00e-29  & 1.21e-32  & 1.13e-05  &           &             \\
      \BILThree{} & 2.72e-05  & 1.33e-02  & 2.44e-01  & 3.65e-43  & 5.68e-35  &             \\
      \BILFour{}  & 2.07e-13  & 1.12e-17  & 6.55e-21  & 3.62e-17  & 6.09e-07  & 1.45e-23    \\
      \toprule
      90-\(\Exp\) & \ql{0.99} & \rl{0.99} & \rl{1.00} & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}   & 2.61e-06  &           &           &           &           &             \\
      \rl{1.00}   & 5.03e-13  & 1.74e-03  &           &           &           &             \\
      \BILOne{}   & 9.64e-23  & 2.73e-33  & 2.22e-39  &           &           &             \\
      \BILTwo{}   & 3.46e-12  & 1.32e-23  & 1.30e-30  & 1.23e-05  &           &             \\
      \BILThree{} & 6.86e-01  & 1.23e-05  & 3.46e-12  & 1.32e-23  & 5.03e-13  &             \\
      \BILFour{}  & 2.45e-04  & 2.38e-01  & 2.60e-05  & 6.39e-31  & 6.30e-21  & 9.46e-4     \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:stats-unif}Results from the statistical analysis for the results of of
    moderate variability in the system. }
\end{table}

>>>>

% \MS[t]{todo} We evaluate two different kinds of reward reporting as they have been proposed by
% \cite{Schneckenreither2019}. They find that it is beneficial to overcome the time offset imposed
% by the production system. That is, although orders are immediately released to the production
% system and thus generate a response in terms of a reward to the agent, the full impact of the
% chosen action takes several periods to materialise. For instance, by deciding not to release an
% order, which later becomes a backorder, it is beneficial to reward the actions actually
% responsible for the backorder instead of the last action (only). Thus they propose to keep track
% of the orders currently in the order pool until all fully traversed through the production system
% and reward the actions according to all orders in the order pool.

@@

      \ql{0.99}      & \cost{38563.000}  & \cost{134703.600} & \cost{81704.800}   & \fgiboc{134703.600}{81704.800}  & \cost{254971.400}$^{1}$  & \timem{1.335} & \fgit{1.335}{2.558} & \tard{0.094} & \costpp{254971.400}  &                    \\

@@

      \rl{1.00}      & \cost{38659.100}  & \cost{156659.200} & \cost{59743.200}   & \fgiboc{156659.200}{59743.200}  & \cost{255061.500}$^{1}$  & \timem{1.338} & \fgit{1.338}{2.678} & \tard{0.068} & \costpp{255061.500}  & \rnd{36.501}       \\

@@

      \rl{1.00}      & \cost{60778.500}  & \cost{234045.000} & \cost{76168.000}   & \fgiboc{234045.000}{76168.000}  & \cost{370991.500}$^{1}$  & \timem{1.637} & \fgit{1.637}{3.226} & \tard{0.066} & \costpp{370991.500}  & \rnd{52.291}       \\

@@

      \BILThree{}    & \cost{51976.550}  & \cost{240175.000} & \cost{77822.400}   & \fgiboc{240175.000}{77822.400}  & \cost{369973.950}$^{1}$  & \timem{1.475} & \fgit{1.475}{3.091} & \tard{0.060} & \costpp{369973.950}  &                    \\

@@

      \ql{0.99}      & \cost{98909.150}  & \cost{190681.000} & \cost{297333.600}  & \fgiboc{190681.000}{297333.600} & \cost{586923.750}$^{1}$  & \timem{2.133} & \fgit{2.133}{3.417} & \tard{0.173} & \costpp{586923.750}  &                    \\
      \rl{0.99}      & \cost{105348.200} & \cost{263950.600} & \cost{207183.200}  & \fgiboc{263950.600}{207183.200} & \textbf{\cost{576482.000}}$^{1}$  & \timem{2.238} & \fgit{2.238}{3.825} & \tard{0.121} & \textbf{\costpp{576482.000}}  & \rnd{79.826}       \\
      \rl{1.00}      & \cost{107873.800} & \cost{240798.800} & \cost{253865.600}  & \fgiboc{240798.800}{253865.600} & \cost{602538.200}$^{2}$  & \timem{2.280} & \fgit{2.280}{3.771} & \tard{0.153} & \costpp{602538.200}  & \rnd{80.425}       \\

@@

      \BILThree{}    & \cost{88252.450}  & \cost{207210.600} & \cost{299885.600}  & \fgiboc{207210.600}{299885.600} & \cost{595348.650}$^{2}$  & \timem{1.957} & \fgit{1.957}{3.309} & \tard{0.148} & \costpp{595348.650}  &                    \\

@@

    distributed demand interarrival times.\newline \(^{1,2}\) Cells marked with the same number are
    not significant different to each other.}

@@

      \ql{0.99}   & \cost{53873.500}  & \cost{142398.800} & \cost{164427.200} & \fgiboc{142398.800}{164427.200} & \cost{360699.500}$^{1}$          & \timem{1.585} & \fgit{1.585}{2.796} & \tard{0.162} & \costpp{360699.500}          &                    \\

@@

      \BILTwo{}   & \cost{48618.850}  & \cost{ 66927.200} & \cost{248638.400} & \fgiboc{ 66927.200}{248638.400} & \cost{364184.450}$^{1}$          & \timem{1.480} & \fgit{1.480}{2.312} & \tard{0.220} & \costpp{364184.450}          &                    \\

@@

      \ql{0.99}   & \cost{87706.700}  & \cost{227485.400} & \cost{225150.400} & \fgiboc{227485.400}{225150.400} & \cost{540342.500}$^{1}$          & \timem{2.043} & \fgit{2.043}{3.541} & \tard{0.166} & \costpp{540342.500}          &                    \\
      \rl{0.99}   & \cost{89838.950}  & \cost{253476.000} & \cost{185687.200} & \fgiboc{253476.000}{185687.200} & \cost{529002.150}$^{1,2}$        & \timem{2.078} & \fgit{2.078}{3.689} & \tard{0.124} & \costpp{529002.150}          & \rnd{70.527}       \\
      \rl{1.00}   & \cost{87171.500}  & \cost{242915.600} & \cost{198456.000} & \fgiboc{242915.600}{198456.000} & \cost{528543.100}$^{2,3}$        & \timem{2.034} & \fgit{2.034}{3.599} & \tard{0.134} & \costpp{528543.100}          & \rnd{72.944}       \\

@@

      \BILThree{} & \cost{79029.850}  & \cost{200273.200} & \cost{242100.800} & \fgiboc{200273.200}{242100.800} & \textbf{\cost{521403.850}}$^{3}$ & \timem{1.890} & \fgit{1.890}{3.265} & \tard{0.142} & \textbf{\costpp{521403.850}} &                    \\

@@

      \ql{0.99}   & \cost{168655.950} & \cost{222145.800} & \cost{788662.400} & \fgiboc{222145.800}{788662.400} & \cost{1179464.150}$^{1}$               & \timem{3.134} & \fgit{3.134}{4.501} & \tard{0.285} & \costpp{1179464.150}         &                    \\
      \rl{0.99}   & \cost{158034.800} & \cost{212726.200} & \cost{701300.800} & \fgiboc{212726.200}{701300.800} & \cost{1072061.800}$^{2}$               & \timem{2.970} & \fgit{2.970}{4.300} & \tard{0.281} & \costpp{1072061.800}         & \rnd{115.801}      \\

@@

      \BILThree{} & \cost{144278.250} & \cost{154146.800} & \cost{877450.400} & \fgiboc{154146.800}{877450.400} & \cost{1175875.450}$^{1}$               & \timem{2.756} & \fgit{2.756}{3.857} & \tard{0.294} & \costpp{1175875.450}         &                    \\
      \BILFour{}  & \cost{147077.800} & \cost{335070.400} & \cost{622141.600} & \fgiboc{335070.400}{622141.600} & \cost{1104289.800}$^{2}$               & \timem{2.800} & \fgit{2.800}{4.608} & \tard{0.175} & \costpp{1104289.800}         &                    \\

@@

    distributed interarrival times of the demand.\newline \(^{1,2,3}\) Cells marked with the same number are
    not significant different to each other. }

@@

* 90-Exp

@@

\section{Statistical Analysis of the Results}

Table~\ref{tbl:stats-unif} and Table~\ref{tbl:stats-exp} provide the statistical results of the
computation results. We used the Friedman test with a significance level of \(p=0.05\) for a
statistical analysis of the mean sum of costs. As expected the omnibus null hypotheses (all samples
are from the same distribution) are rejected for all cases. Therefore, we conducted pairwise Conover
post-hoc tests adjusted by the Benjaminyi-Hochberg FDR method~\citep{benjamini1995controlling} to
reduce liberality. These results are shown in Table~\ref{tbl:stats-unif} and
Table~\ref{tbl:stats-exp} for the uniformly and exponentially distributed interarrival times of the
demand respectively. The values given in bold are below the significance level of \(5\%\) and
therefore indicate which row-column tuples are not statistically significant.

\begin{table}
  \begin{center}
    \begin{tabular}{lP{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}}
      \toprule
      70-\(\Unif\) & \ql{0.99}         & \rl{0.99} & \rl{1.00}         & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 3.37e-04          &           &                   &           &           &             \\
      \rl{1.0}     & \textbf{3.55e-01} & 1.04e-05  &                   &           &           &             \\
      \BILOne{}    & 1.94e-45          & 2.48e-51  & 6.90e-44          &           &           &             \\
      \BILTwo{}    & 1.09e-24          & 3.35e-16  & 9.57e-27          & 3.66e-64  &           &             \\
      \BILThree{}  & 1.78e-20          & 9.27e-29  & 2.44e-18          & 1.35e-22  & 6.26e-47  &             \\
      \BILFour{}   & 6.30e-34          & 3.85e-41  & 4.83e-32          & 1.16e-08  & 3.00e-56  & 1.16e-08    \\
      \bottomrule
      \toprule
      80-\(\Unif\) & \ql{0.99}         & \rl{0.99} & \rl{1.00}         & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & 4.78e-16          &           &                   &           &           &             \\
      \rl{1.00}    & 5.26e-04          & 3.96e-08  &                   &           &           &             \\
      \BILOne{}    & 1.02e-40          & 1.98e-21  & 3.92e-34          &           &           &             \\
      \BILTwo{}    & 6.98e-10          & 7.12e-03  & 2.06e-03          & 1.31e-27  &           &             \\
      \BILThree{}  & 2.16e-02          & 8.93e-11  & \textbf{2.03e-01} & 1.57e-36  & 2.46e-05  &             \\
      \BILFour{}   & 6.16e-33          & 1.10e-11  & 2.74e-25          & 5.33e-05  & 5.38e-18  & 5.30e-28    \\
      \bottomrule
      \toprule
      90-\(\Unif\) & \ql{0.99}         & \rl{0.99} & \rl{1.00}         & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}    & \textbf{5.18e-01} &           &                   &           &           &             \\
      \rl{1.00}    & 1.94e-04          & 1.56e-05  &                   &           &           &             \\
      \BILOne{}    & 8.40e-42          & 9.61e-43  & 1.10e-34          &           &           &             \\
      \BILTwo{}    & 2.36e-33          & 1.10e-34  & 5.21e-25          & 1.56e-05  &           &             \\
      \BILThree{}  & 4.16e-04          & 3.64e-05  & \textbf{8.19e-01} & 6.27e-35  & 1.81e-25  &             \\
      \BILFour{}   & 2.33e-20          & 6.57e-22  & 1.79e-11          & 2.93e-18  & 4.39e-08  & 5.97e-12    \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:stats-unif}P-Values from the statistical analysis for the results of
    moderate variability in the system. Tuples marked bold are not significantly different.}
\end{table}

\begin{table}
  \begin{center}
    \begin{tabular}{lP{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}P{1.75cm}}
      \toprule
      70-\(\Exp\) & \ql{0.99}         & \rl{0.99}         & \rl{1.00}         & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}   & 1.75e-02          &                   &                   &           &           &             \\
      \rl{1.00}   & 6.15e-07          & 5.50e-12          &                   &           &           &             \\
      \BILOne{}   & 7.62e-35          & 1.74e-39          & 1.32e-23          &           &           &             \\
      \BILTwo{}   & \textbf{3.33e-01} & 1.02e-03          & 3.17e-05          & 6.06e-33  &           &             \\
      \BILThree{} & 5.96e-17          & 1.79e-11          & 6.09e-29          & 7.00e-52  & 3.47e-19  &             \\
      \BILFour{}  & 1.16e-24          & 6.25e-30          & 1.68e-12          & 4.68e-06  & 1.56e-22  & 3.43e-44    \\
      \bottomrule
      \toprule
      80-\(\Exp\) & \ql{0.99}         & \rl{0.99}         & \rl{1.00}         & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}   & \textbf{7.07e-02} &                   &                   &           &           &             \\
      \rl{1.00}   & 1.74e-03          & \textbf{1.72e-01} &                   &           &           &             \\
      \BILOne{}   & 2.39e-35          & 6.77e-39          & 2.38e-41          &           &           &             \\
      \BILTwo{}   & 1.22e-25          & 1.00e-29          & 1.21e-32          & 1.13e-05  &           &             \\
      \BILThree{} & 2.72e-05          & 1.33e-02          & \textbf{2.44e-01} & 3.65e-43  & 5.68e-35  &             \\
      \BILFour{}  & 2.07e-13          & 1.12e-17          & 6.55e-21          & 3.62e-17  & 6.09e-07  & 1.45e-23    \\
      \bottomrule
      \toprule
      90-\(\Exp\) & \ql{0.99}         & \rl{0.99}         & \rl{1.00}         & \BILOne{} & \BILTwo{} & \BILThree{} \\
      \midrule
      \rl{0.99}   & 2.61e-06          &                   &                   &           &           &             \\
      \rl{1.00}   & 5.03e-13          & 1.74e-03          &                   &           &           &             \\
      \BILOne{}   & 9.64e-23          & 2.73e-33          & 2.22e-39          &           &           &             \\
      \BILTwo{}   & 3.46e-12          & 1.32e-23          & 1.30e-30          & 1.23e-05  &           &             \\
      \BILThree{} & \textbf{6.86e-01} & 1.23e-05          & 3.46e-12          & 1.32e-23  & 5.03e-13  &             \\
      \BILFour{}  & 2.45e-04          & \textbf{2.38e-01} & 2.60e-05          & 6.39e-31  & 6.30e-21  & 9.46e-4     \\
      \bottomrule
    \end{tabular}
  \end{center}
  \caption{\label{tbl:stats-exp}P-Values from the statistical analysis for the results of
    high variability in the system. Tuples marked bold are not significantly different.}
\end{table}
